Deriving Multi-headed Planar Dependency Parses from Link Grammar Parses

### 2014-05-20 doc/LinksToDAG.tex
removed LinksToDAG.sty. Redownloaded acl2014.sty and added it to the repo.
changed LinksToDAG.bst to acl2014.bst
moved exampleSentence.tikz to sentences.tikz
added smallcaps to everything in a math equation

\documentclass[11pt]{article}
\usepackage{LinksToDAG}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{soul}
\newcommand{\Note}[1]{}
\renewcommand{\Note}[1]{\hl{[#1]}}  % comment out this definition to suppress all Notes                                                                                
\newcommand{\TODO}[1]{\Note{TODO: #1}}
\newcommand{\NoteSigned}[3]{{\sethlcolor{#2}\Note{#1: #3}}}
\newcommand{\NoteJE}[1]{\NoteSigned{JE}{LightBlue}{#1}}
\newcommand{\NoteJH}[1]{\NoteSigned{JH}{YellowGreen}{#1}}

@@

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=\linewidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Precision and Recall of different runs on English}
\end{figure}

@@

@@

@@

\bibliographystyle{LinksToDAG}
\bibliography{LinksToDAG}

>>>>

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{soul}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{tikz-dependency}

\newcommand{\Note}[1]{}
\renewcommand{\Note}[1]{\hl{[#1]}}  % comment out this definition to suppress all Notes                                                                                
\newcommand{\TODO}[1]{\Note{TODO: #1}}
\newcommand{\NoteSigned}[3]{{\sethlcolor{#2}\Note{#1: #3}}}
\newcommand{\NoteJE}[1]{\NoteSigned{JE}{LightBlue}{#1}}
\newcommand{\NoteJH}[1]{\NoteSigned{JH}{YellowGreen}{#1}}

@@

\begin{equation}
  count_{L, \textsc{left}} = \sum_{a \in \textsc{ARCS}_L} left_a
\end{equation}
\begin{equation}
  count_{L, \textsc{left}} = \textsc{M} \cdot \textsc{allowed}_{L,\textsc{left}} + \textsc{slack}_{L}
\end{equation}
Where $L \in \textsc{LABELS}$, and $\textsc{M}$ is the size of the corpus.
The objective is:
\begin{equation}
  \min \sum_{L \in \textsc{LABELS} \atop \textsc{DIR} \in \{left, right\}} (\textsc{allowed}_{L,\textsc{DIR}}) \atop + \textsc{COST}(L) * \sum_L \textsc{slack}_L
\end{equation}
\begin{equation}
  \textsc{COST}(L) = \frac{100}{(\textsc{count}_{L,\textsc{left}} + \textsc{count}_{L,\textsc{right}})}
\end{equation}

@@

\begin{figure}[ht!]
  \includegraphics[width=\linewidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Precision and Recall of different runs on English}
\end{figure}

@@

\section{Link Corpus}

Compared to the original conll data, the link parses match about half the conll arcs in location and directionality. The mismatches in the other half can be accounted for in the following ways.

\subsection{Blanks}
Whenever the link parser failed to recognize a word from its dictionary, it would skip it and fail to attach any links. This accounts for about 10\% of the mismatches.

\subsection{Directional Mismatches}
In about 25\% of the cases, the conll arc's corresponding link would be assigned the opposite direction.

@@

\begin{figure*}[ht!]
  \centering
  \input{figure/sentences.tikz}
  \caption{Example Sentences}
\end{figure*}

@@

\bibliographystyle{acl2014}
\bibliography{LinksToDAG}
